Visualizations for article

### 2016-05-26 101-visualizations-for-article.Rmd
Yet more color updates

matches_to_NY <- all_matches %>% 
  filter(borrower_code == "NV1861",
         str_detect(match_code, "NY"),
         match_code != "NY1829",
         score >= 0.1,
         match_year <= 1861) %>% 
  group_by(borrower_section) %>% 
  arrange(desc(score)) %>% 
  slice(1) %>% 
  ungroup()

@@

matches_to_NY <- all_matches %>% 
  filter(borrower_code == "IA1859",
         str_detect(match_code, "NY"),
         match_code != "NY1829",
         score >= 0.1,
         match_year <= 1859) %>% 
  group_by(borrower_section) %>% 
  arrange(desc(score)) %>% 
  slice(1) %>% 
  ungroup()

>>>>

matches_to_NY <- all_matches %>% 
  filter(borrower_code == "NV1861",
         str_detect(match_code, "NY"),
         match_code != "NY1829",
         score >= 0.1,
         match_year <= 1861) %>% 
  group_by(borrower_section) %>% 
  filter(score >= max(score) - 0.1) %>% 
  arrange(desc(match_code)) %>% 
  slice(1) %>% 
  ungroup()

@@

matches_to_NY <- all_matches %>% 
  filter(borrower_code == "IA1859",
         str_detect(match_code, "NY"),
         match_code != "NY1829",
         score >= 0.1,
         match_year <= 1859) %>% 
  group_by(borrower_section) %>% 
  filter(score >= max(score) - 0.1) %>% 
  arrange(desc(match_code)) %>% 
  slice(1) %>% 
  ungroup()
